Code Notes

### 2018-12-03 code_notes.Rmd
update code_notes

```{r}
install.packages("tidyverse")
install.packages(c("devtools", "roxygen2", "testthat", "knitr"))
install.packages("devtools")
library(devtools)
devtools::install_github("nwfsc-assess/geostatistical_delta-GLMM")
install.packages("INLA", repos=c(getOption("repos"), INLA="https://inla.r-inla-download.org/R/stable"), dep=TRUE)
```

@@

>>>>

```{r}
# install.packages("tidyverse")
# install.packages(c("devtools", "roxygen2", "testthat", "knitr"))
# install.packages("devtools")
# library(devtools)
# devtools::install_github("nwfsc-assess/geostatistical_delta-GLMM")
# install.packages("INLA", repos=c(getOption("repos"), INLA="https://inla.r-inla-download.org/R/stable"), dep=TRUE)
```

@@

```{r eval=False}
library(tidyverse)
tidyverse_update()
```
